\mytitle

### 2021-12-20 paper.tex
typo
extend text

Algorithm 327 \cite{koelbigDilog}, Algorithm 490 \cite{ginsberg} and
the implementation found in the Gnu Scientific Library (GSL)
\cite{gsl} use series expansions, which are summed using Horner's
scheme.  These algorithms thus do not make use of ILP, which is one
reason for their longer runtime.  Furthermore, Algorithm 490 and most
series expansions in the GSL use floating\-/point divisions inside
loops, which may be another reason for the increased runtime.

% Chebyshev \cite{luke,root}

>>>>

Algorithm 327 \cite{koelbigDilog}, Algorithm 490 \cite{ginsberg} and
the implementation found in the GNU Scientific Library (GSL)
\cite{gsl} use series expansions, which are summed using Horner's
scheme.  These algorithms thus do not make use of ILP, which is one
reason for their longer runtime.  Furthermore, Algorithm 490 and most
series expansions in the GSL use floating\-/point divisions inside
loops, which may be another reason for the increased runtime.

A representation in terms of Chebyshev polynomials \cite{luke} is
implemented in the ROOT program library \cite{root}.  In this
implementation the polynomials are summed using Clenshaw's algorithm,
which is also purely sequencial and slightly more complex than
Horner's scheme.  This is a reason why the implementation in
\cite{root} has a larger runtime than the rational function
approximants discussed above.
